Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-15 paper/manuscript.Rmd
edit paragraph 1

The Fogo Island archipelago, off the coast of Newfoundland, Canada, is home to
approximately 300 woodland caribou. During routine fieldwork on May 30, 2017, we
observed an unmarked adult male caribou swim between two small islands (Figure
1, see Figure 2 for location), a distance of at least 470 m which took ~9
minutes (~52 m per minute). Residents of Fogo Island confirmed this phenomenon
and have also reported regularly observing caribou swimming between islands.
This observation prompted us to investigate whether swimming behaviour was
common among GPS radio-collared caribou in the population [n = 29, for collaring
details see, @Peignier2019]. We identified an individual's swimming events as
two consecutive GPS locations (2-hour relocation rates)  on different islands.
Northeastern Newfoundland typically experiences pack ice during winter and
caribou are known locally to travel between islands by walking over the ice. We
restricted our GPS data to the ice-free period of the year (April 1 to December
31) and identified `r nevents` swimming events over three years (Figure 2).

<!-- That first paragraph would benefit from a bit of signpost at its end to
let us know what kind of ideas you're going go talk about near the end. -->

>>>>

The Fogo Island archipelago, off the coast of Newfoundland, Canada, is home to
approximately 300 woodland caribou. During routine fieldwork on May 30, 2017, we
observed an unmarked adult male caribou swim between two small islands (Figure 1
& 2), a distance of at least 470 m which took ~9 minutes (~52 m per minute).
Residents of Fogo Island confirmed this phenomenon and have also reported
regularly observing caribou swimming between islands. This observation prompted
us to investigate whether swimming behaviour was common among GPS radio-collared
caribou in the population [n = 29, for collaring details see, @Peignier2019]. We
identified an individual's swimming events as two consecutive GPS locations
(2-hour relocation rates) on different islands. Newfoundland typically
experiences pack ice in late winter and caribou ,may travel between islands by
walking over the ice. To identify swimming events, we restricted our dataset
between April 1 and December 31 and identified `r nevents` swimming events over
three years (Figure 2). Given the prevalence of swimming in this population, we
discuss the causes and consequences of this behaviour and propose future areas
of research.
